Towards Bringing Together Numerical Methods for Partial Differential Equation and Image Processing

### 2020-05-07 paper/paper.tex
Final touches

We adopt the objective for the discriminator network and we modify it slightly by leaving out the random vector $z$.
\begin{equation}
  \mathcal{L}_{cGAN} (G, D) = (\mathbb{E}[\log D (x,y)] + \mathbb{E}[\log D (x, G(x))])/2 \\
  = (\log D (x,y) + \log D (x, G(x)))/2
\end{equation}
where $x$ is the input image and $y$ is the target image. We leave out the expected value calculation as we do not use the random vector $z$ in our objective. In contrast to unconditional GANs, both the generator and the discriminator network have access to the input image. The objective is divided by two to slow down the training of the discriminator relative to the generator as suggested by~\cite{pix2pix}.

@@

\begin{table}[H]
  \begin{center}
    Inflow speed model
  \end{center}
  \begin{center}
    \begin{tabular}{l|cc|cc}
     \textbf{Frame} & \multicolumn{2}{c|} {\shortstack{\textbf{Start index: 120}\\$g=1.9487$}}& \multicolumn{2}{c}{\shortstack{\textbf{Start index: 120}\\$g=3.9358$}}\\
      \hline 
                     &\multicolumn{2}{c|}{} & &\\
                     & {Average difference} & {Max difference}  &  {Average difference} & {Max difference}\\
      \emph{Frame 1}       &34.27(0.02) & 52.72(0.40)    &35.91(0.02) & 51.76(0.38)   \\
      \emph{Frame 5}       &33.86(0.11) & 60.41(1.62)    &35.84(0.10) & 53.13(0.54)   \\
      \emph{Frame 10}      &33.99(0.17) & 66.04(2.16)    &36.01(0.15) & 54.59(1.14)   \\
      \emph{Frame 15}      &33.80(0.20) & 76.40(3.67)    &35.91(0.20) & 58.90(1.97)   \\
      \emph{Frame 20}      &34.27(0.22) & 75.39(3.07)    &35.89(0.24) & 62.60(2.94)   \\
      \emph{Frame 25}      &33.91(0.22) & 83.45(3.06)    &35.93(0.28) & 61.07(2.60)   \\
      \emph{Frame 30}      &34.13(0.24) & 79.15(2.20)    &35.73(0.33) & 66.69(4.21)   \\
      \emph{Frame 35}      &34.38(0.23) & 83.52(2.09)    &35.94(0.35) & 65.55(4.18)   \\      
    \end{tabular}
  \end{center}
  \caption{Again, all of the numbers are in percents and are averaged across the evaluations of models trained only with difference in the used seed. The standard deviation is given in the parenthesis. To note is that the maximum difference is high for almost all frames. This is to be expected from our models as they primarily target the visual quality of the results. The average difference on the other hand stays relatively stable across the frames. Still, average difference of over 30\% unsatisfactory even for coarse simulation.}\label{tab:recursive_inflow}
\end{table}

@@

\noindent\textbf{Performance:} All of the models were evaluated on an Nvidia GTX 980Ti GPU.\@In all cases, the forward propagation of a single simulation frame took between 5 and 20 ms (milliseconds). In comparison, during the data generation, HiFlow needed between 1000 and 1500 ms for a single simulation timestep while using 12 MPI processes. This does not include the time needed for rendering the results of the simulation. To note is that this is not a one-to-one comparison as HiFlow runs on the CPU and uses MPI and OpenMP for parallelization. Also, we performed all the real simulations with HiFlow on a Intel Xeon E5-2650 v4 CPU.

>>>>

We adopt the objective function the discriminator network and we modify it slightly by leaving out the random vector $z$.
\begin{equation}
  \begin{split}
    \mathcal{L}_{cGAN} (G, D) &= (\mathbb{E}[\log D (x,y)] + \mathbb{E}[\log D (x, G(x))])/2 \\
    &= (\log D (x,y) + \log D (x, G(x)))/2
  \end{split}
\end{equation}
where $x$ is the input image and $y$ is the target image. We leave out the expected value calculation as we do not use the random vector $z$ in our loss function. In contrast to unconditional GANs, both the generator and the discriminator network have access to the input image. The objective is divided by two to slow down the training of the discriminator relative to the generator as suggested by~\cite{pix2pix}.

@@

\begin{table}[H]
  \begin{center}
    Inflow speed model
  \end{center}
  \begin{center}
    \begin{tabular}{l|cc|cc}
     \textbf{Frame} & \multicolumn{2}{c|} {\shortstack{\textbf{Start index: 120}\\$g=1.9487$}}& \multicolumn{2}{c}{\shortstack{\textbf{Start index: 120}\\$g=3.9358$}}\\
      \hline 
                     &\multicolumn{2}{c|}{} & &\\
                     & {Average difference \%} & {Max difference \%}  &  {Average difference \%} & {Max difference \%}\\
      \emph{Frame 1}       &34.27(0.02) & 52.72(0.40)    &35.91(0.02) & 51.76(0.38)   \\
      \emph{Frame 5}       &33.86(0.11) & 60.41(1.62)    &35.84(0.10) & 53.13(0.54)   \\
      \emph{Frame 10}      &33.99(0.17) & 66.04(2.16)    &36.01(0.15) & 54.59(1.14)   \\
      \emph{Frame 15}      &33.80(0.20) & 76.40(3.67)    &35.91(0.20) & 58.90(1.97)   \\
      \emph{Frame 20}      &34.27(0.22) & 75.39(3.07)    &35.89(0.24) & 62.60(2.94)   \\
      \emph{Frame 25}      &33.91(0.22) & 83.45(3.06)    &35.93(0.28) & 61.07(2.60)   \\
      \emph{Frame 30}      &34.13(0.24) & 79.15(2.20)    &35.73(0.33) & 66.69(4.21)   \\
      \emph{Frame 35}      &34.38(0.23) & 83.52(2.09)    &35.94(0.35) & 65.55(4.18)   \\      
    \end{tabular}
  \end{center}
  \caption{Again, all of the numbers are in percents and are averaged across the evaluations of models trained only with difference in the used seed. The standard deviation is given in the parenthesis. To note is that the maximum difference is high for almost all frames. This is to be expected from our models as they primarily target the visual quality of the results. The average difference on the other hand stays relatively stable across the frames. Still, average difference of over 30\% unsatisfactory even for coarse simulation.}\label{tab:recursive_inflow}
\end{table}

@@

\noindent\textbf{Performance:} All of the models were evaluated on an Nvidia GTX 980Ti GPU.\@In all cases, the forward propagation of a single simulation frame took between 5 and 20 ms (milliseconds). In comparison, during the data generation, HiFlow needed between 1000 and 1500 ms for a single simulation timestep while using 12 MPI processes. This does not include the time needed for rendering the results of the simulation. To note is that this is not a one-to-one comparison as HiFlow runs on the CPU and uses MPI and OpenMP for parallelization. In our case the used CPU was Intel Xeon E5-2650 v4.
